Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-12-13 main.tex
:pencil: Update energy detection

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
% \usepackage[subtle]{savetrees}

@@

@@

			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set. For tag $k$ at state $m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			which denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge. For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} We also define $z \triangleq \lVert \boldsymbol{y} \rVert^2$ as the received signal energy over $N$ primary blocks, and $f(z \mid \mathcal{H}_i)$ as the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Correspondingly, $z$ is the sum of $N$ i.i.d. exponential variables each with mean $\sigma_i^2$, and thus follows Erlang distribution with shape $N$ and scale $\sigma_i^2$
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
				\label{eq:energy_distribution}
			\end{equation}

			\begin{remark}
				The backscatter links essentially create a discrete-input continuous-output memoryless channel. To further reduce decoding complexity, we apply hard-decision detection and formulate a Discrete Memoryless Thresholding Channel (DMTC), whose capacity is a function of both input distribution and decision thresholds.
			\end{remark}

			For example, consider the Maximum-Likelihood (ML) detector where the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,j}^{\mathrm{ML}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			and the corresponding decision rule is
			\begin{equation}
				\Lambda_{i,j}^{\mathrm{ML}}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j}^{\mathrm{ML}},
				\label{eq:decision_rule}
			\end{equation}
			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
			\begin{equation}
				T_{i,j}^{\mathrm{ML}} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2},
				\label{eq:detection_threshold}
			\end{equation}
			and we manually define $T_{0,1}^{\mathrm{ML}} \triangleq 0$ and $T_{M^K,M^K+1}^{\mathrm{ML}} \triangleq \infty$. Let $\mathcal{T}^{\mathrm{ML}} \triangleq \{T_{0,1}^{\mathrm{ML}},\ldots,T_{M^K,M^K+1}^{\mathrm{ML}}\}$.

			\begin{remark}
				Although the ML decision threshold set $\mathcal{T}^{\mathrm{ML}}$ is optimal in terms of the likelihood function, it is not necessarily the same with the capacity-achieving threshold set $\mathcal{T}^{\star}$. Interestingly, it was shown in \cite{Qian2019b} that $\mathcal{T}^{\mathrm{ML}}$ and $\mathcal{T}^{\star}$ are very close in the single-tag BIBO case.
			\end{remark}

			For any given threshold set $\mathcal{T} \triangleq \{T_{0,1},\ldots,T_{M^K,M^K+1}\}$, the decision region of hypothesis $\mathcal{H}_i$ is
			\begin{equation}
				\mathcal{R}_i \triangleq [T_{i-1,i}, T_{i,i+1}),
				\label{eq:decision_region}
			\end{equation}
			which can be combined with \eqref{eq:energy_distribution} to formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix. The probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Is this necessary? Maybe we can keep those same energy levels and avoid them by input distribution design.}
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:point_to_point_channel}
			\end{equation}

			Based on the equivalent point-to-point channel \eqref{eq:point_to_point_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. Hence, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, for every tag input combination with fixed threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
		\end{subsection}

		\begin{subsection}{Backscatter sum-rate}
			Before investigating the sum-rate of the tags, we introduce some prerequisites in information theory. Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, such that $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Following \cite{Rezaeian2004}, the information function associated with specific tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
			\begin{equation}
				I(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
				\label{eq:information_function}
			\end{equation}
			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is written as
			\begin{equation}
				I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
				\label{eq:marginal_information_function}
			\end{equation}
			and the mutual information of the tags and the received signal can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
			\begin{equation}
				I(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
				\label{eq:mutual_information}
			\end{equation}

			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$. Therefore, we can obtain the backscatter sum-rate by maximizing the mutual information over the tag input distributions as
			\begin{equation}
				R_c = \max_{P(c_{\mathcal{K}})} I(c_{\mathcal{K}} ; z) \ [\si{bpcu}].
				\label{eq:backscatter_sum_rate}
			\end{equation}
		\end{subsection}

		\begin{subsection}{Primary ergodic rate}
			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully decoded, the user can eliminate the backscatter uncertainty and model it within the equivalent primary channel by \eqref{eq:equivalent_primary_channel}. For primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. As such, the ergodic primary rate can be expressed as
			\begin{align}
				R_s
				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right) \ [\si{bps/Hz}].
				\label{eq:primary_ergodic_rate}
			\end{align}
			which is also a function of the tag input distribution $P(c_{\mathcal{K}})$.
		\end{subsection}
	\end{section}

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary ergodic-secondary sum rate region}
			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the tag input distribution, decision region, and precoder to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
			\begin{maxi!}
				{\scriptstyle{P(c_{\mathcal{K}}),\mathcal{T},\boldsymbol{w}}}{\rho R_s + (1 - \rho) R_c}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P\label{co:average_transmit_power}}
				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
			\end{maxi!}
			where $\rho \in [0,1]$ denotes the priority of the primary link. As problem \eqref{op:rate_region} is not jointly convex over $P(c_{\mathcal{K}})$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose an Block Coordinate Descent (BCD)-based algorithm that iteratively updates the input distribution, decision region, and precoder, until convergence.
		\end{subsection}

		\begin{subsection}{Input distribution}
			Once the decision region boundaries $\mathcal{T}$ and the precoder $\boldsymbol{w}$ are determined, we can obtain the equivalent discrete memoryless MAC by \eqref{eq:mac}. [The optimal solution is obtained in closed form; to add here]
		\end{subsection}

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[acronym]{glossaries-extra}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
% \usepackage[subtle]{savetrees}

@@

\setabbreviationstyle[acronym]{long-short}

\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}

@@

			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set. For tag $k$ at state $m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			which denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$.
			% It can be numerically evaluated based on the precoder, tag, channel, and noise knowledge.
			For the ease of exposition, we denote the hypothesis that the tag input combination at status $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Correspondingly, $z$ is the sum of $N$ i.i.d. exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
				\label{eq:energy_distribution}
			\end{equation}

			\begin{remark}
				The backscatter links essentially form a discrete-input continuous-output memoryless channel. To further reduce decoding complexity, we apply hard-decision detection and construct a Discrete Memoryless Thresholding Channel (DMTC), whose capacity is a function of both input distribution and decision thresholds \cite{Nguyen2018}.
			\end{remark}

			Denote the decision region of hypothesis $\mathcal{H}_i$ as
			\begin{equation}
				\mathcal{R}_i \triangleq [T_{i-1,i}, T_{i,i+1}),
				\label{eq:decision_region}
			\end{equation}
			where $T_{i-1,i}$ is the decision threshold between $\mathcal{H}_{i-1}$ and $\mathcal{H}_i$, and $T_{i,i+1}$ is the decision threshold between $\mathcal{H}_i$ and $\mathcal{H}_{i+1}$. We also define $T_{0,1} \triangleq 0$, $T_{M^K,M^K+1} \triangleq \infty$, and $\mathcal{T} \triangleq \{T_{0,1},\ldots,T_{M^K,M^K+1}\}$.

			Consider the Maximum-Likelihood (ML) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			and the corresponding decision rule is
			\begin{equation}
				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,{i'}}^{\mathrm{ML}},
				\label{eq:decision_rule}
			\end{equation}
			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is
			\begin{equation}
				T_{i,{i'}}^{\mathrm{ML}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
				\label{eq:detection_threshold}
			\end{equation}

			\begin{remark}
				Although the ML decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag BIBO case.
			\end{remark}

			Once the decision region is determined, we can formulate an equivalent point-to-point DMC from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$. The probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Merge with precoder design.}
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:point_to_point_channel}
			\end{equation}

			On top of this, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. The probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, with CSI knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
		\end{subsection}

		\begin{subsection}{Backscatter sum-rate}
			Before investigating the sum-rate of the tags, we introduce some prerequisites of information theory. Define the input probability distribution of tag $k$ at status $m_k$ as $P_k(\bar{c}_{m_k})$, and assume the input distribution of all tags are mutually independent, i.e., $P_{\mathcal{K}}(\bar{c}_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Following \cite{Rezaeian2004}, the backscatter information function associated with tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
			\begin{equation}
				I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)},
				\label{eq:information_function}
			\end{equation}
			the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is written as
			\begin{equation}
				I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{\mathcal{K} \setminus \mathcal{S}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
				\label{eq:marginal_information_function}
			\end{equation}
			and the mutual information of the tags and the received signal can be expressed as\footnote{Please be aware that $c_{\mathcal{K}}$, $c_{\mathcal{S}}$, $z$ are random variables, while $\bar{c}_{m_{\mathcal{K}}}$ (and $\bar{c}_i$), $\bar{c}_{m_{\mathcal{S}}}$, $\bar{z}_j$ represent the corresponding instances.}
			\begin{equation}
				I_{\mathrm{B}}(c_{\mathcal{K}} ; z) = \mathbb{E}_{c_{\mathcal{K}}} \left[I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)\right] = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathrm{B},\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
				\label{eq:mutual_information}
			\end{equation}

			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $P_k(\bar{c}_{m_k})$, $\forall m_k \in \mathcal{M}$, $\forall k \in \mathcal{K}$. Therefore, the mutual information of the tags can be explicitly written as
			\begin{equation}
				I_{\mathrm{B}}(c_{\mathcal{K}} ; z) = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \sum_j P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(\bar{z}_j)}.
				\label{eq:backscatter_sum_rate}
			\end{equation}

			% we can explicitly write the mutual information as

			% obtain the backscatter sum-rate by maximizing the mutual information over the tag input distributions as
			% \begin{equation}
			% 	R_c = \max_{P(c_{\mathcal{K}})} I(c_{\mathcal{K}} ; z) \ [\si{bpcu}].
			% 	\label{eq:backscatter_sum_rate}
			% \end{equation}
		\end{subsection}

		\begin{subsection}{Primary ergodic rate}
			Once the tag symbol set $\bar{c}_{m_{\mathcal{K}}}$ is successfully decoded, the user can eliminate the backscatter uncertainty and model it within the equivalent primary channel by \eqref{eq:equivalent_primary_channel}. For primary transmission, the tags adjust the propagation environment in a potentially beneficial manner, and create artificial channel variation within each fading block. As such, the ergodic primary mutual information can be expressed as
			\begin{align}
				I_{\mathrm{P}}
				& = \mathbb{E}_{c_{\mathcal{K}}} \left[\log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right)\right]\nonumber\\
				& = \sum_{m_{\mathcal{K}}} \prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k}) \log_2 \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_w^2}\right) \ [\si{bps/Hz}].
				\label{eq:primary_ergodic_rate}
			\end{align}
			which is also a function of the tag input distribution $P(c_{\mathcal{K}})$.
		\end{subsection}
	\end{section}

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary ergodic-secondary sum rate region}
			To achieve a flexible tradeoff between the primary and backscatter links, we aim to optimize the tag input distribution, decision region, and precoder to maximize the weighted sum of the ergodic primary rate and the total backscatter rate, under the average transmit power and probability constraints
			\begin{maxi!}
				{\scriptstyle{P(c_{\mathcal{K}}),\mathcal{T},\boldsymbol{w}}}{I \triangleq \rho I^{\mathrm{P}} + (1 - \rho) I^{\mathrm{B}}}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P\label{co:average_transmit_power}}
				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
			\end{maxi!}
			where $\rho \in [0,1]$ denotes the priority of the primary link. As problem \eqref{op:rate_region} is not jointly convex over $P(c_{\mathcal{K}})$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose an Block Coordinate Descent (BCD)-based algorithm that iteratively updates the input distribution, decision region, and precoder, until convergence.
		\end{subsection}

		\begin{subsection}{Input distribution}
			Once the decision boundaries $\mathcal{T}$ and the precoder $\boldsymbol{w}$ are determined, obtain the equivalent discrete memoryless MAC by \eqref{eq:mac}. The input distribution optimization subproblem is
			\begin{maxi!}
				{\scriptstyle{P(c_{\mathcal{K}})}}{I}{\label{op:input_distribution}}{\label{ob:weighted_sum_rate_input_distribution}}
				\addConstraint{\sum_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability_input_distribution}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability_input_distribution}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
			\end{maxi!}

			Although the domain is non-convex for $K>1$, the \gls{kkt} conditions are sufficient and necessary for an input distribution to achieve the weighted sum-capacity. The proof follows straightforwardly from \cite{Watanabe2009} and details are omitted here.\footnote{For any elementary MAC (the sizes of input alphabets are no greater than that of the output alphabet), the sufficiency can be proved by local maximum and connectedness of \gls{kkt} solutions. Also, the capacity of an arbitrary MAC is achieved by an elementary MAC included within.}
			% We restrict the discussion of this paper to elementary MACs.
